A Study of the Effectiveness of Usage Examples in REST API Documentation

### 2017-03-26 controlled_study.tex
add the confidence interval info

\subsubsection{Data Analysis}
We analyzed the data artifact qualitatively to understand the obstacles that REST API client developers face when using an API documentation that lacks usage examples. We exported a table of data from the database behind web-based REST API explorer. For each row, the table contains the following columns: API task, participant identifier, timestamp, API trial number, I1-4, response headers and body. It allowed us to observe and categorize the different input values that the participants used to perform the given API tasks. The values for I1-4 used by the participants were manually coded to group the participant responses into categories. The categories help us determine the types of information that API client developers need in the API documentation to perform API tasks successfully. The analysis started with an empty set of codes and new codes were introduced to describe scenarios that did not fall under  codes that were already applied. The first author applied the codes on the raw data artifact and the co-authors verified the codes randomly. To resolve disagreements, the authors discussed and updated the codes accordingly. The codes were then further categorized to higher level grouping to represent common problems faced by the study participants for each group.

>>>>

\subsubsection{Data Analysis}
We analyzed the data artifact qualitatively to understand the obstacles that REST API client developers face when using an API documentation that lacks usage examples. We exported a table of data from the database behind web-based REST API explorer. For each row, the table contains the following columns: API task, participant identifier, timestamp, API trial number, I1-4, response headers and body. The values for I1-4 used by the participants were manually coded to group the participant responses into categories. The categories help us determine the types of information that API client developers need in the API documentation to perform API tasks successfully. The analysis started with an empty set of codes and new codes were introduced to describe scenarios that did not fall under  codes that were already applied. The first author applied the codes on the raw data artifact and provided a coding scheme to a co-author. The co-author applied the codes to 82/539 (10\% confidence interval with 95\% confidence level) API calls made by the participants. To resolve disagreements, the authors discussed and updated the codes accordingly.
